---
title: "Analysing Congreve & Lamsdell matrices"
author: "Martin R. Smith <martin.smith@durham.ac.uk>"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: yes
    includes:
      in_header: ../inst/preamble.tex
bibliography: ../inst/REFERENCES.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/dependent/biology-letters.csl
link-citations: yes
github-repo: ms609/Quartet
vignette: >
  %\VignetteIndexEntry{Data analysis protocol}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The files required to reproduce these analyses are included in the R
package directory on installation, and can be downloaded from [Github](https://github.com/ms609/CongreveLamsdell2016/tree/master/inst).

If you have [RStudio](https://www.rstudio.com/), you can open the R Markdown
file used to generate this document (`vignettes/Conduct-analyses.Rmd`) to run the
R scripts that will copy all necessary files and begin analyses on your 
behalf.  You will need to specify some paths for automatic downloading:
```{R}
# Directory in which to install MrBayes
BAYES_DIR <- "C:/Research/MrBayes"

# Directory in which to conduct parsimony analysis
HOME <- "C:/Research/iw" # Must not end in a trailing '/'

# GitHub remote
INST_ROOT <- "https://raw.githubusercontent.com/ms609/CongreveLamsdell2016/master/inst/"
```



## Bayesian analysis

###bayesgen.pl — Generate MrBayes files

A Perl script to execute analysis using Markov models in MrBayes.

The script reads the datasets of Congreve and Lamsdell [-@Congreve2016], appends a MrBayes block to the Nexus files, and executes a MrBayes run, saving the consensus trees and preparing them for analysis in R.

Before running the script:

*	[Install MrBayes](http://mrbayes.sourceforge.net/)
```{r eval=FALSE}
MRBAYES_RELEASE <- "https://github.com/NBISweden/MrBayes/releases/download/v3.2.6/MrBayes-3.2.6_WIN32_x64.zip"
zipFile <- paste0(BAYES_DIR, '/MrBayes.zip')
download.file(MRBAYES_RELEASE, destfile=zipFile, method='auto', mode='wb')
unzip(zipFile, c('MrBayes/mrbayes_x64.exe', 'MrBayes/mrbayes_x86.exe'), 
      exdir=BAYES_DIR, junkpaths=TRUE)
file.remove(zipFile)
```

*	Download Appendix S5 from Congreve and Lamsdell [-@Congreve2016dd] 
(doi:[10.5061/dryad.7dq0j/5](https://dx.doi.org/10.5061/dryad.7dq0j/5)) and unzip its 100 nexus files to a local directory (default: `C:/Research/MrBayes/iw`)
```{r eval=FALSE}
tempFile <- tempfile(fileext='.zip')
download.file("https://datadryad.org/bitstream/handle/10255/dryad.108351/S5%20-%20Character%20Weights%20Test%20NEXUS%20files.zip", tempFile)
unzip(tempFile, exdir=paste0(BAYES_DIR, '/iw'), junkpaths=TRUE,
      files = paste0('Weights tests/', formatC(1:100, width=3, flag=0), '.txt.nex'))
file.remove(tempFile)
```

*	Copy `mrbayesblock.nex` to the `iw` directory, and 
  `bayesgen.pl` and `t2nex.pl` to the root MrBayes directory.  
  Modify the latter files to specify path to MrBayes (default: `C:/Research/MrBayes/`)
  and path to extracted matrices (default: `C:/Research/MrBayes/iw`)
```{r eval=FALSE}
download.file(paste0(INST_ROOT, "analysis-bayesian/mrbayesblock.nex"), 
              paste0(BAYES_DIR, '/iw/mrbayesblock.nex'))
              
bayesGenPath <- paste0(BAYES_DIR, '/bayesgen.pl')
download.file(paste0(INST_ROOT, "analysis-bayesian/bayesgen.pl"), bayesGenPath)
bayesGen <- readLines(bayesGenPath)
bayesGen[5] <- paste0('$dir = "', BAYES_DIR, '/iw";')
bayesGen[6] <- paste0('$bayes_dir = "', BAYES_DIR, '";')
writeLines(bayesGen, bayesGenPath)

t2nexPath <- paste0(BAYES_DIR, '/t2nex.pl')
download.file(paste0(INST_ROOT, "analysis-bayesian/t2nex.pl"), t2nexPath)
t2nex <- readLines(t2nexPath)
t2nex[2] <- paste0('$dir = "', BAYES_DIR, '/iw";')
writeLines(t2nex, t2nexPath)
```


## Parsimony analysis

###mptgen.pl — Generate parsimony trees in TNT

A Perl script to generate most parsimonious trees by parsimony search in TNT.

The script generates TNT scripts to perform parsimony analysis on each of the Congreve and Lamsdell datasets, under equal and implied weights, with and without suboptimal trees.
It then executes these scripts and converts the output into a format suitable for analysis in R.

Before running the script, you'll need an installation of Perl.  [Strawberry Perl](http://strawberryperl.com/) works on MS Windows.

Then:

*	Create a local directory (default: `C:/Research/iw`) with subdirectories 
  entitled `Matrices`, and `Trees`.  Then, within the new `Trees` directory, 
  create the further subdirectories `eq`, `k1`, `k2`, `k3`, `k5` and `kX`.

```{r eval=FALSE}
sapply(paste0(HOME, '/', c('', 'Matrices', 'Trees')), dir.create)
sapply(paste0(HOME, '/Trees/', c('eq', 'k1', 'k2', 'k3', 'k5', 'kX')), dir.create)
```

*	[Install TNT](http://www.lillo.org.ar/phylogeny/tnt/).

```{r eval=FALSE, message=FALSE}
zipFile <- paste0(HOME, '/TNT.ZIP')
# This is the Windows path; use the appropriate path for your operating system
download.file("http://www.lillo.org.ar/phylogeny/tnt/ZIPCHTNT.ZIP", 
              destfile=zipFile, method='auto', mode='wb')
unzip(zipFile, 'tnt.exe', exdir=HOME)
file.remove(zipFile)
```

*	Copy `mptgen.pl` and (optinally) `tnt2nex.pl` into this root directory, updating each file so its variable $dir corresponds to the appropriate path.  
`tnt2nex.pl` translates TNT output into NEXUS format and may be useful if you 
wish to perform further analysis of TNT output.  This will be performed
automatically if you uncomment the final line of `mptgen.pl`.

```{r eval=FALSE}
tnt2nexPath <-  paste0(HOME, '/tnt2nex.pl')
mptgenPath <-  paste0(HOME, '/mptgen.pl')

download.file(paste0(INST_ROOT, "analysis-parsimony/tnt2nex.pl"), tnt2nexPath)
tnt2nex <- readLines(tnt2nexPath)
tnt2nex[3] <- paste0('$dir = "', HOME, '/Trees";')
writeLines(tnt2nex, tnt2nexPath)

download.file(paste0(INST_ROOT, "analysis-parsimony/mptgen.pl"), mptgenPath)
mptgen <- readLines(mptgenPath)
mptgen[3] <- paste0('$dir = "', HOME, '";')
writeLines(mptgen, mptgenPath)
```

*	Copy the file `tnt_template.run` into the root directory.

```{r eval=FALSE}
download.file(paste0(INST_ROOT, "analysis-parsimony/tnt_template.run"), 
              paste0(HOME, '/tnt_template.run'))
```

*	Download Appendix S1 from Congreve and Lamsdell [-@Congreve2016dd]  (doi:[10.5061/dryad.7dq0j/1](https://dx.doi.org/10.5061/dryad.7dq0j/1)) and unzip its 100 text files to `Matrices`.

```{r eval=FALSE}
tempFile <- tempfile(fileext='.zip')
download.file("https://datadryad.org/bitstream/handle/10255/dryad.101095/S1%20-%20TNT%20files.zip", tempFile)
unzip(tempFile, exdir=paste0(HOME, '/Matrices'))
```

* Perform the analyses by executing `mptgen.pl`. (Once Perl is installed,
you can just double-click the file.)
